Kolmogorov-Smirnov

### 2020-04-09 article.tex
Show PDF if TeX is edited
Make figure 1 and table

\begin{figure}[!htbp]
  \includegraphics[width=0.4\textwidth]{pics/ks.png}
  \caption{
    Condition of a Kolmogorov-Smirnov (KS) statistic to rejects a null
    hypothesis. $D_{n,m}$ is the KS statistic, $n = m$ is the size
    of the samples, in this case, the number of HLA haplotypes ($n = m = 13$).
    $\alpha = 0.05$ is the significance level.
  }
  \label{fig:ks}
\end{figure}

@@

Transmembrane helices and strong MHC-II-binding peptides
were predicted for a tuberculosis reference proteome 
from \url{https://www.ebi.ac.uk/reference_proteomes}
using the \verb;epitopeome; R package (\cite{epitopeome}).
We picked the three MHC-II alleles that are most abundant 
in the current human population, 
which are DRB4*0101, HLA-DPA10103-DPB10402 
\richel{
  We decided for DPB1*0402, but there are multiple alleles matching.
  I just picked the first one of the alleles matching, which are:
  HLA-DPA10x-DPB10402, where x equals 103-110, 201-204, 301-303 or 401
}
and DQA1*0501/DQB1*0301 \richel{reference here}.
The 5\% peptides with the lowest IC50 values were defined as binders.
We then simply counted the number of amino acids that were present inside the
cell, within the membrane or outside of the cell, as well as if it was part 
of a strong MHC-II binding site, as shown in figue \ref{tab:results}.

The \verb;epitopeome; R package (\cite{epitopeome}) binds 
together the \verb;tmhmm; (\cite{tmhmm}) and \verb;netmhc2pan; 
(\cite{netmhc2pan}) 
R packages. \verb;tmhmm; provides an R interface to
TMHMM (\cite{krogh2001predicting, sonnhammer1998hidden}), a tool
to predict where membrane proteins' amino acids are located within the
membrance.   
\verb;netmhc2pan; provides an R interface to
NetMHC2pan (\cite{jensen2018improved}), a tool
to predict MHC-II binding to proteins.

@@

The evolutionary conservation of TMHs was measured from a
DNA alignment of multiple transmembrane proteins in multitiple
species of the mycoplasma bacterial family
\richel{how obtained exactly? how alignment done?}.

@@

For each alignment, the inference model with the highest evidence
is used in a Bayesian inference. From each Bayesian posterior,
the parameter estimates regarding mutation rates (including clock rate)
were obtained and compared to determine which realized mutation rate is lower.
The Markov chain Monte Carlo was set up in such a way that the effective sample
size for the likelihood of the inference model is above the recommended value
of 200 (\cite{bouckaert2014beast}).

@@

Table \ref{tab:results} shows the location and binding strength for the
tuberculosis proteome.

@@

The Bayesian inference resulted in [a distribution of mutation rates],
as shown in [absent figure].
The ESSes of the Bayesian parameter estimates was above 200, exact values
are shown in tables \ref{tab:esses_tmh} and \ref{tab:esses_non_tmh}.

@@

\appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model selection}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[ht]
\centering
\begin{tabular}{rlllrr}
  \hline
 & Site model & Clock model & Tree prior & log(evidence) & Weight \\ 
  \hline
1 & JC & Strict & Yule & -8201.109 & 0.002 \\ 
  2 & JC & Strict & BD & -8203.346 & 0.000 \\ 
  3 & JC & Strict & CCP & -8195.927 & 0.278 \\ 
  4 & JC & Strict & CEP & -8194.976 & 0.720 \\ 
   \hline
\end{tabular}
\caption{
  Evidences for the TMH-only alignment
  \richel{These are just example values}
} 
\label{tab:evidences_tmh}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rlllrr}
  \hline
 & Site model & Clock model & Tree prior & log(evidence) & Weight \\ 
  \hline
1 & JC & Strict & Yule & -8201.109 & 0.002 \\ 
  2 & JC & Strict & BD & -8203.346 & 0.000 \\ 
  3 & JC & Strict & CCP & -8195.927 & 0.278 \\ 
  4 & JC & Strict & CEP & -8194.976 & 0.720 \\ 
   \hline
\end{tabular}
\caption{
  Evidences for the non-TMH alignment
  \richel{These are just example values}
} 
\label{tab:evidences_non_tmh}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Inference strength}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & posterior & likelihood & prior & treeLikelihood & TreeHeight & YuleModel & 
birthRate \\ 
  \hline
1 & 10001 & 10001 & 10001 & 10001 & 9913 & 10001 & 9540 \\ 
   \hline
\end{tabular}
\caption{
  ESSes of the TMH-only alignment
  \richel{These are just example values}
} 
\label{tab:esses_tmh}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & posterior & likelihood & prior & treeLikelihood & TreeHeight & YuleModel & 
birthRate \\ 
  \hline
1 & 10001 & 10001 & 10001 & 10001 & 9913 & 10001 & 9540 \\ 
   \hline
\end{tabular}
\caption{
  ESSes of the non-TMH alignment
  \richel{These are just example values}
} 
\label{tab:esses_non_tmh}
\end{table}

>>>>

\begin{figure}[!htbp]
  \includegraphics[width=0.4\textwidth]{ks/fig_1.png}
  \caption{
    Condition of a Kolmogorov-Smirnov (KS) statistic to rejects a null
    hypothesis. $D_{n,m}$ is the KS statistic, $n = m$ is the size
    of the samples, in this case, the number of HLA haplotypes ($n = m = 13$).
    $\alpha = 0.05$ is the significance level.
  }
  \label{fig:ks}
\end{figure}

@@

\iffalse
	Transmembrane helices and strong MHC-II-binding peptides
	were predicted for a tuberculosis reference proteome 
	from \url{https://www.ebi.ac.uk/reference_proteomes}
	using the \verb;epitopeome; R package (\cite{epitopeome}).
	We picked the three MHC-II alleles that are most abundant 
	in the current human population, 
	which are DRB4*0101, HLA-DPA10103-DPB10402 
	\richel{
	  We decided for DPB1*0402, but there are multiple alleles matching.
	  I just picked the first one of the alleles matching, which are:
	  HLA-DPA10x-DPB10402, where x equals 103-110, 201-204, 301-303 or 401
	}
	and DQA1*0501/DQB1*0301 \richel{reference here}.
	The 5\% peptides with the lowest IC50 values were defined as binders.
	We then simply counted the number of amino acids that were present inside the
	cell, within the membrane or outside of the cell, as well as if it was part 
	of a strong MHC-II binding site, as shown in figue \ref{tab:results}.

	The \verb;epitopeome; R package (\cite{epitopeome}) binds 
	together the \verb;tmhmm; (\cite{tmhmm}) and \verb;netmhc2pan; 
	(\cite{netmhc2pan}) 
	R packages. \verb;tmhmm; provides an R interface to
	TMHMM (\cite{krogh2001predicting, sonnhammer1998hidden}), a tool
	to predict where membrane proteins' amino acids are located within the
	membrance.   
	\verb;netmhc2pan; provides an R interface to
	NetMHC2pan (\cite{jensen2018improved}), a tool
	to predict MHC-II binding to proteins.
\fi

@@

\iffalse
	The evolutionary conservation of TMHs was measured from a
	DNA alignment of multiple transmembrane proteins in multitiple
	species of the mycoplasma bacterial family
	\richel{how obtained exactly? how alignment done?}.

@@

	For each alignment, the inference model with the highest evidence
	is used in a Bayesian inference. From each Bayesian posterior,
	the parameter estimates regarding mutation rates (including clock rate)
	were obtained and compared to determine which realized mutation rate is lower.
	The Markov chain Monte Carlo was set up in such a way that the effective sample
	size for the likelihood of the inference model is above the recommended value
	of 200 (\cite{bouckaert2014beast}).
\fi

@@

\iffalse
	Table \ref{tab:results} shows the location and binding strength for the
	tuberculosis proteome.

@@

	The Bayesian inference resulted in [a distribution of mutation rates],
	as shown in [absent figure].
	The ESSes of the Bayesian parameter estimates was above 200, exact values
	are shown in tables \ref{tab:esses_tmh} and \ref{tab:esses_non_tmh}.
\fi

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Supplementary materials}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Binding}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{ks/table_1.latex}

### 2020-04-09 ks/ks.Rmd
Make figure 1 and table

```{r}
sink("table_1.latex")
  xtable::print.xtable(
    xtable::xtable(
      df,
      caption = paste0("Percentage of epitopes overlapping \nwith transmembrane helix"),
      digits = 2
    ),
    include.rownames = FALSE
  )
sink()
```

>>>>

```{r}
sink("table_1.latex")
  xtable::print.xtable(
    xtable::xtable(
      df,
      caption = paste0("Percentage of epitopes overlapping \nwith transmembrane helix"),
      digits = 3
    ),
    include.rownames = FALSE
  )
sink()
```
